---
title: "Exploring ToothData"
output: html_document
---
#ToothData Problem 2
###Load the ToothGrowth data and perform some basic exploratory data analyses 
###Provide a basic summary of the data.
Below is the loading of the data along with some basic exploration and summarization
```{r}
data("ToothGrowth")
summary(ToothGrowth)
str(ToothGrowth)
```
The len column shows the length of teeth in each of 10 guinea pigs at each of three dose levels of Vitamin C (0.5, 1, and 2 mg) in the dose column with each of two delivery methods (orange juice or ascorbic acid) in the supp column
###Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose. (Use the techniques from class even if there's other approaches worth considering)

The results brlow show a low p-value for each dose level, and since the p-value is very low, we reject the null hypothesis. There is strong evidence of a mean increase in tooth growth between Ascorbic Acid and Orange Juice.
```{r}
t5 <- ToothGrowth[ToothGrowth$dose == 0.5,]
t10 <- ToothGrowth[ToothGrowth$dose == 1.0,]
t20 <- ToothGrowth[ToothGrowth$dose == 2.0,]

t.test(t5$len[t5$supp == "OJ"], t5$len[t5$supp == "VC"], paired=TRUE, alternative="greater")
t.test(t10$len[t10$supp == "OJ"], t5$len[t10$supp == "VC"], paired=TRUE, alternative="greater")
t.test(t20$len[t20$supp == "OJ"], t5$len[t20$supp == "VC"], paired=TRUE, alternative="greater")
```