#Exponential Distribution

##Simulate data
Per the assignment, set lambda equal to .2.  We will then simulate 1000 n=40 samples and take the mean of each.  This will be stored in a vector called "means"

```{r}
lambda <- .2
n <- 40
nosim <- 1000
means <- NULL

for (i in 1:1000) {
        means[i] <- mean(rexp(n, lambda))
}
```

##Explore the data
###1. Show where the distribution is centered at and compare it to the theoretical center of the distribution.
The distribution is centered at:
```{r}
mean(means)
```
The theoretical center is $1/\lambda$ which is:

```{r}
1/lambda
```

###2. Show how variable it is and compare it to the theoretical variance of the distribution.
Because the Central Limit Thoerim applies, the theoretical variance is $\sigma^2 / n$

Using this, we can compare the distribution variance:
```{r}
var(means)
```

To the theoretical variance:
```{r}
((1/lambda)^2)/n
```


###3. Show that the distribution is approximately normal.
We can use qqnorm to test for a normality.  qqnorm per it's description produces a normal QQ plot of the values in y. qqline adds a line to a “theoretical”, by default normal, quantile-quantile plot which passes through the probs quantiles, by default the first and third quartiles.

```{r}
qqnorm(y=means); qqline(y=means, col=2)
```

As you can see, the values are very close to a normal distribution

